---
title: "Clusia pratensis drought study using constructed bacterial communities"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 4
    
---

# Packages 
```{r}
library(tidyverse)
library(plotrix)
library(car)
library(ggpubr)

mytheme <- theme_classic(base_size = 12) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

# Biomass Measurements
```{r Biomass Dataset}
biomass <- read.csv("~/Documents/Git/clusia_droughtexperiment/GrowthMeasurements.csv", header = TRUE, stringsAsFactors = TRUE, na.strings = "NA")
biomass <- biomass %>% 
  arrange(Condition, Treatment, SampleNumber) %>% 
  filter(Treatment != "Control Mock")
```

## Controls
No difference between Control plants and plants that were inoculated with autoclaved bacteria (Control Mock). Confirms that the inoculation process itself does not account for changes between control plants and sample plants. 

```{r}
controls <- biomass %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock")
```

## Soil water
```{r}
soilwater.control <- aov(SoilWater ~ Condition * Treatment, data = controls)
summary(soilwater.control) # no difference between control and control mock 
```

## Total Dry Mass
```{r}
totaldrywt.control <- aov(Total_DryWt ~ Condition * Treatment, data = controls)
summary(totaldrywt.control) # no difference between control and control mock 
```

## Root biomass
```{r}
rootbiomass.control <- aov(RootBiomass ~ Condition * Treatment, data = controls)
summary(rootbiomass.control) # no difference between control and control mock
```

## Root:Shoot 
```{r}
rootshoot.control <- aov(RootShoot ~ Condition * Treatment, data = controls)
summary(rootshoot.control) # slight interaction term, but negligible
```

## RMF
```{r}
rmf.control <- aov(RMF ~ Condition * Treatment, data = controls)
summary(rmf.control)

# removing control mock
biomass <- biomass %>%
  filter(Treatment != "Control Mock")
```


## Summary Stats by Water Treatment
```{r}
biomass.sum <- biomass %>% 
  group_by(Condition) %>% 
  summarise_at(c("ShootBiomass", "Total_DryWt", "RootBiomass", "RootShoot", "RMF"), funs(mean, sd, std.error))

# mean shoot biomass
mean_shootbiomass <- ggplot(data = biomass.sum, aes(x = Condition, y = ShootBiomass_mean)) + geom_bar(stat = "identity", colour = "black") + geom_errorbar(aes(ymin = ShootBiomass_mean-ShootBiomass_std.error, ymax = ShootBiomass_mean+ShootBiomass_std.error), width = 0.2) + mytheme + ylab("Mean Shoot Biomass (g DW)") + theme(axis.title.x = element_blank())

pdf("mean_shootbiomass_box.pdf")
plot(mean_shootbiomass)
dev.off()

# mean root biomass
mean_rootbiomass <- ggplot(data = biomass.sum, aes(x = Condition, y = RootBiomass_mean)) + geom_bar(stat = "identity", colour = "black") + geom_errorbar(aes(ymin = RootBiomass_mean-RootBiomass_std.error, ymax = RootBiomass_mean+RootBiomass_std.error), width = 0.2) + mytheme + ylab("Mean Root Biomass (g DW)") + theme(axis.title.x = element_blank())

pdf("mean_rootbiomass_box.pdf")
plot(mean_rootbiomass)
dev.off()

# mean total dry mass
mean_totaldrymass <- ggplot(data = biomass.sum, aes(x = Condition, y = Total_DryWt_mean)) + geom_bar(stat = "identity", colour = "black") + geom_errorbar(aes(ymin = Total_DryWt_mean-Total_DryWt_std.error, ymax = Total_DryWt_mean+Total_DryWt_std.error), width = 0.2) + mytheme + ylab("Mean Total Biomass (g DW)") + theme(axis.title.x = element_blank())

pdf("mean_totaldrymass_box.pdf")
plot(mean_totaldrymass)
dev.off()

# mean RootShoot
mean_rootshoot <- ggplot(data = biomass.sum, aes(x = Condition, y = RootShoot_mean)) + geom_bar(stat = "identity", colour = "black") + geom_errorbar(aes(ymin = RootShoot_mean-RootShoot_std.error, ymax = RootShoot_mean+RootShoot_std.error), width = 0.2) + mytheme + ylab("Mean Root:Shoot") + theme(axis.title.x = element_blank())

pdf("mean_rootshoot_box.pdf")
plot(mean_rootshoot)
dev.off()

# mean rmf 
mean_rmf <- ggplot(data = biomass.sum, aes(x = Condition, y = RMF_mean)) + geom_bar(stat = "identity", colour = "black") + geom_errorbar(aes(ymin = RMF_mean-RMF_std.error, ymax = RMF_mean+RMF_std.error), width = 0.2) + mytheme + ylab("Mean RMF") + theme(axis.title.x = element_blank())

pdf("mean_rmf_box.pdf")
plot(mean_rmf)
dev.off()
```

## Summary Stats by Water Tratment x Microbial Treatment
```{r}
biomass.sum2 <- biomass %>% 
  group_by(Condition, Treatment) %>% 
  summarise_at(c("ShootBiomass", "Total_DryWt", "RootBiomass", "RootShoot", "RMF"), funs(mean, sd, std.error))
View(biomass.sum2)

# mean shoot biomass
mean_shoot_isolates <- ggplot(data = biomass.sum2, aes(x = Treatment, y = ShootBiomass_mean, fill = Condition)) + geom_bar(stat = "identity", colour = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = ShootBiomass_mean-ShootBiomass_std.error, ymax = ShootBiomass_mean+ShootBiomass_std.error), width = 0.2, position = position_dodge(0.9)) + mytheme + ylab("Mean Shoot Biomass (g DW)") + theme(axis.title.x = element_blank()) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.9)) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)) + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates"))

pdf("mean_shootisolates_box.pdf")
plot(mean_shoot_isolates)
dev.off()

# mean root biomass
mean_rootisolates <- ggplot(data = biomass.sum2, aes(x = Treatment, y = RootBiomass_mean, fill = Condition)) + geom_bar(stat = "identity", colour = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = RootBiomass_mean-RootBiomass_std.error, ymax = RootBiomass_mean+RootBiomass_std.error), width = 0.2, position = position_dodge(0.9)) + mytheme + ylab("Mean Root Biomass (g DW)") + theme(axis.title.x = element_blank()) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.9)) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)) + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates"))

pdf("mean_rootisolates_box.pdf")
plot(mean_rootisolates)
dev.off()

# mean total dry mass
mean_totalisolates <- ggplot(data = biomass.sum2, aes(x = Treatment, y = Total_DryWt_mean, fill = Condition)) + geom_bar(stat = "identity", colour = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = Total_DryWt_mean-Total_DryWt_std.error, ymax = Total_DryWt_mean+Total_DryWt_std.error), width = 0.2, position = position_dodge(0.9)) + mytheme + ylab("Mean Total Biomass (g DW)") + theme(axis.title.x = element_blank()) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.9)) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)) + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates"))

pdf("mean_totalisolates_box.pdf")
plot(mean_totalisolates)
dev.off()

# mean root shoot
mean_rootshoot_isolates <- ggplot(data = biomass.sum2, aes(x = Treatment, y = RootShoot_mean, fill = Condition)) + geom_bar(stat = "identity", colour = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = RootShoot_mean-RootShoot_std.error, ymax = RootShoot_mean+RootShoot_std.error), width = 0.2, position = position_dodge(0.9)) + mytheme + ylab("Mean Root:Shoot") + theme(axis.title.x = element_blank()) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.9)) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)) + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates"))

pdf("mean_rootshootisolates.pdf")
plot(mean_rootshoot_isolates)
dev.off()

# mean rmf
mean_rmfisolates <- ggplot(data = biomass.sum2, aes(x = Treatment, y = RMF_mean, fill = Condition)) + geom_bar(stat = "identity", colour = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = RMF_mean-RMF_std.error, ymax = RMF_mean+RMF_std.error), width = 0.2, position = position_dodge(0.9)) + mytheme + ylab("Mean RMF") + theme(axis.title.x = element_blank()) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)) + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates"))

pdf("mean_rmfisolates.pdf")
plot(mean_rmfisolates)
dev.off()

```

## Boxplots
### Shoot Biomass
```{r}
# condition
cond.shoot <- ggplot(data = biomass, aes(x = Condition, y = ShootBiomass)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + ylab("Biomass (g DW)") + theme(axis.title.x = element_blank()) + scale_y_continuous(limits = c(0, 50))

pdf("cond_shoot.pdf")
plot(cond.shoot)
dev.off()

# condition x treatment
cond.treat.shoot <- ggplot(data = biomass, aes(x = Treatment, y = ShootBiomass, fill = Condition)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.85)) + ylab("Shoot Biomass (g DW)") + xlab("Constructed Community") + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates")) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)) + scale_y_continuous(limits = c(0, 50))

pdf("cond_treat_shoot.pdf")
plot(cond.treat.shoot)
dev.off()
```

### Total Biomass
```{r}
# condition
cond_totalbiomass <- ggplot(data = biomass, aes(x = Condition, y = Total_DryWt)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + ylab("Biomass (g DW)") + scale_y_continuous(limits = c(0, 200)) + theme(axis.title.x = element_blank())

pdf("cond_totalbiomas.pdf")
plot(cond_totalbiomass)
dev.off()

# condition x treatment
cond_treat_totalbiomass <- ggplot(data = biomass, aes(x = Treatment, y = Total_DryWt, fill = Condition)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.85)) + ylab("Biomass (g DW)") + xlab("Constructed Community") + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates")) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)) + scale_y_continuous(limits = c(0, 200))

pdf("cond_treat_totalbiomass.pdf")
plot(cond_treat_totalbiomass)
dev.off()
```

### Root biomass
```{r}
# condition
cond_root <- ggplot(data = biomass, aes(x = Condition, y = RootBiomass)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + ylab("Root Biomass (g DW)") + scale_y_continuous(limits = c(0, 200)) + theme(axis.title.x = element_blank())

pdf("cond_root.pdf")
plot(cond_root)
dev.off()

# condition x treatment
cond_treat_root <- ggplot(data = biomass, aes(x = Treatment, y = RootBiomass, fill = Condition)) + geom_boxplot() + mytheme + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.85)) + ylab("Root Biomass (g DW)") + xlab("Constructed Community") + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates")) + scale_y_continuous(limits = c(0, 200)) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1))

pdf("cond_treat_root")
plot(cond_treat_root)
dev.off()

```

Possible trend in both total biomass and root biomass is that both Drought and Phosphorus communities have consistently higher means than the control, nonfunctional isolates, and all isolates plants. Although not statistically significant, they suggest that there may be an advantage to the plants to have specifically these specialized constructed communities during drought conditions. 

### Root:Shoot
```{r}
# condition
cond_rootshoot <- ggplot(data = biomass, aes(x = Condition, y = RootShoot)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + ylab("Root:Shoot") + scale_y_continuous(limits = c(0, 20)) + theme(axis.title.x = element_blank())

pdf("cond_rootshoot.pdf")
plot(cond_rootshoot)
dev.off()

# condition x treatment
cond_treat_rootshoot <- ggplot(data = biomass, aes(x = Treatment, y = RootShoot, fill = Condition)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.85)) + ylab("Root : Shoot") + xlab("Constructed Community") + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates")) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1))

pdf("cond_treat_rootshoot.pdf")
plot(cond_treat_rootshoot)
dev.off()
```

### Root Mass Fraction
```{r}
# condition
cond_rmf <- ggplot(data = biomass, aes(x = Condition, y = RMF)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + ylab("RMF") + scale_y_continuous(limits = c(0.0, 1.0)) + theme(axis.title.x = element_blank())

pdf("cond_rmf.pdf")
plot(cond_rmf)
dev.off()

# condition x treatment
cond_treat_rmf <- ggplot(data = biomass, aes(x = Treatment, y = RMF, fill = Condition)) + geom_boxplot() + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(legend.position = c(0.13, 0.2)) + ylab("Root Mass Fraction") + xlab("Constructed Community") + scale_x_discrete(limits = c("Control", "Nonfunctional Isolates", "Drought Isolates", "Phosphorus Isolates", "All Isolates")) + theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)) + scale_y_continuous(limits = c(0.0, 1.0))

pdf("cond_treat_rmf.pdf")
plot(cond_treat_rmf)
dev.off()
```

## ANOVAs
### Soil Water
```{r}
soilwater.aov <- aov(SoilWater ~ Condition*Treatment, data = biomass)
summary(soilwater.aov) 

# homogeneity of variance
plot(soilwater.aov, 1) 
leveneTest(SoilWater ~ Condition*Treatment, data = biomass) 

# testing normality
plot(soilwater.aov, 2)
water.residuals <- residuals(object = soilwater.aov)
shapiro.test(x = water.residuals) 

ggplot(data = biomass, aes(x = Treatment, y = SoilWater)) + geom_boxplot() + facet_grid(. ~ Condition) + mytheme
```

### Total Dry Mass
```{r Total Dry Mass Histogram & ANOVA}

# density histogram
ggplot(data = biomass, aes(x = Total_DryWt)) + geom_histogram(aes(y=..density..), binwidth = 15, color="black", fill="gray") + geom_density(alpha = 0.2, fill = "#FF6666") + theme_classic() + xlab("Biomass (g DW)") + ylab("Density") + mytheme + ggtitle("Total Dry Mass Density Histogram")

# histogram by Condition (water treatment)
mu <- biomass %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(Total_DryWt))

ggplot(data = biomass, aes(x = Total_DryWt, fill = Condition)) + geom_histogram(binwidth = 15, position = "identity", alpha = 0.5) + geom_vline(data = mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Biomass (g DW)") + ylab("Count") + theme(legend.position = c(0.9, 0.9)) + ggtitle("Total Dry Mass Histogram")

totaldrywt.aov <- aov(Total_DryWt ~ Condition*Treatment, data = biomass)
summary(totaldrywt.aov) 

# homogeneity of variance
plot(totaldrywt.aov, 1)
leveneTest(Total_DryWt ~ Condition*Treatment, data = biomass) 

# testing normality
plot(totaldrywt.aov, 2
     )
totaldrywt.residuals <- residuals(object = totaldrywt.aov)
shapiro.test(x = totaldrywt.residuals) 
```

```{r Total Dry Mass Normality & Outliers}

# identifying outliers
mod <- lm(Total_DryWt ~ Condition, data = biomass)
cooksd <- cooks.distance(mod)

plot(cooksd, pch="*", cex = 2, main = "Influential Obs in Total Dry Mass by Cooks Distance")
abline(h = 4*mean(cooksd, na.rm = T), col = "red")
text(x = 1: length(cooksd)+1, y = cooksd, labels = ifelse(cooksd>4*mean(cooksd, na.rm = T), names(cooksd), ""), col = "red")

# identifying rows with the outliers
biomass.out <- as.numeric(names(cooksd)[(cooksd > 4*mean(cooksd, na.rm = T))])

# removing outliers and testing impact
biomass <- biomass[-c(67,72), ]

ggqqplot(biomass$Total_DryWt)
shapiro.test(biomass$Total_DryWt) # completely normal

# biomass total dry weight is now normal.
# rerunning biomass anova with removed outliers
totaldrywt.aov <- aov(Total_DryWt ~ Condition*Treatment, data = biomass)
summary(totaldrywt.aov) # same conclusion
```

### Root Biomass
```{r Root Biomass Histogram & ANOVA}

# density histogram
ggplot(data = biomass, aes(x = RootBiomass)) + geom_histogram(binwidth = 8, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") + mytheme + ggtitle("Root Biomass Density Diagram")

# by water treatment
mu2 <- biomass %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(RootBiomass))

ggplot(data = biomass, aes(x = RootBiomass, fill = Condition)) + geom_histogram(binwidth =9, position = "identity", alpha = 0.5) + geom_vline(data = mu2, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Root Biomass (g DW)") + ylab("Count") + theme(legend.position = c(0.9, 0.9)) + mytheme + ggtitle("Root Biomass Histogram")

# ANOVA
rootbiomass.aov <- aov(RootBiomass ~ Condition*Treatment, data = biomass)
summary(rootbiomass.aov) 

# homogeneity of variance
plot(rootbiomass.aov, 1)
leveneTest(RootBiomass ~ Condition*Treatment, data = biomass) 

# normality test
plot(rootbiomass.aov, 2)
rootbiomass.residuals <- residuals(object = rootbiomass.aov)
shapiro.test(x = rootbiomass.residuals)

```

```{r Root Biomass Normality & Outliers}

# identifying outliers
mod2 <- lm(RootBiomass ~ Condition, data = biomass)
cooksd2 <- cooks.distance(mod2)

plot(cooksd2, pch = "*", cex = 2, main = "Influential Observations in Root Biomass")
abline(h = 4*mean(cooksd2, na.rm = T), col = "red")
text(x=1: length(cooksd2) + 1, y= cooksd2, labels = ifelse(cooksd2>4*mean(cooksd2, na.rm = T), names(cooksd2), ""), col = "red")

# same samples are causing the irregularity
rootbiomass.out <- as.numeric(names(cooksd2)[(cooksd2 > 4*mean(cooksd2, na.rm = T))])
head(biomass[rootbiomass.out, ])

# removing outliers and testing impact
biomass <- biomass[-c(67,72), ]

ggqqplot(biomass$RootBiomass)
shapiro.test(biomass$RootBiomass)
```

### Root:Shoot
```{r Root:Shoot Histogram & ANOVA}
# density histogram
ggplot(data = biomass, aes(x = RootShoot)) + geom_histogram(binwidth = 0.8, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") + mytheme + ggtitle("Root:Shoot Density Histogram")

# by water treatment
mu3 <- biomass %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(RootShoot))

ggplot(data = biomass, aes(x = RootShoot, fill = Condition)) + geom_histogram(binwidth = 0.8, position = "identity", alpha = 0.5) + geom_vline(data = mu3, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("RootShoot") + ylab("Count") + theme(legend.position = c(0.9, 0.9)) + mytheme + ggtitle("Root:Shoot Histogram")

# ANOVA
rootshoot.aov <- aov(RootShoot ~ Condition*Treatment, data = biomass)
summary(rootshoot.aov) 

# homogeneity of variance
plot(rootshoot.aov, 1) 
leveneTest(RootShoot ~ Condition*Treatment, data = biomass)

# normality test
plot(rootshoot.aov, 2)
rootshoot.residuals <- residuals(object = rootshoot.aov)
shapiro.test(x = rootshoot.residuals) 

```

```{r Root:Shoot Normality & Outliers}

# identifying outliers
mod3 <- lm(RootShoot ~ Condition, data = biomass)
cooksd3 <- cooks.distance(mod3)

plot(cooksd3, pch = "*", cex = 2, main = "Influential Observations in RootShoot")
abline(h = 4*mean(cooksd3, na.rm = T), col = "red")
text(x=1: length(cooksd3) + 1, y= cooksd3, labels = ifelse(cooksd3>4*mean(cooksd3, na.rm = T), names(cooksd3), ""), col = "red")

rootbiomass.out <- as.numeric(names(cooksd3)[(cooksd3 > 4*mean(cooksd3, na.rm = T))])
head(biomass[rootbiomass.out, ])

# removing outliers and testing impact
biomass.rootshoot <- biomass[-c(10,42, 51, 54), ]

ggqqplot(biomass.rootshoot$RootShoot)
shapiro.test(biomass.rootshoot$RootShoot)
```

### RMF
```{r Histogram & ANOVA}
# density histogram
ggplot(data = biomass, aes(x = RMF)) + geom_histogram(binwidth = 0.03, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") + mytheme + ggtitle("Root Mass Fraction Density Histogram")

# by water treatment
mu4 <- biomass%>% 
  group_by(Condition) %>% 
  summarise(mean = mean(RMF))

ggplot(data = biomass, aes(x = RMF, fill = Condition)) + geom_histogram(binwidth = 0.03, position = "identity", alpha = 0.5) + geom_vline(data = mu4, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Root Mass Fraction") + ylab("Count") + theme(legend.position = c(0.9, 0.9)) + mytheme + ggtitle("Root Mass Fraction Histogram")

# ANOVA
rmf.aov <- aov(RMF~ Condition*Treatment, data = biomass)
summary(rmf.aov) 

# homogeneity of variance
plot(rmf.aov, 1)
leveneTest(RMF ~ Condition*Treatment, data = biomass) 

# normality test
plot(rmf.aov, 2)
rmf.residuals <- residuals(object = rmf.aov)
shapiro.test(x = rmf.residuals) 

```
Note: Root mass fraction = mass of fine root (g) / total biomass (g)

# Physiology Measurements
##  Malic Acid Titrations
```{r Malic Acid Data}
clusia.malic <- read.csv("~/Documents/Git/clusia_droughtexperiment/MalicAcid.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
```

### Malic Acid Controls
```{r Malic Acid Controls}
# Week 0
wk0.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_0") %>% 
  arrange(Condition, Treatment)

malic.control0.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk0.controls)
summary(malic.control0.aov) # not sigificant between autoclaved and inoculated controls

# Week 2
wk2.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_2") %>% 
  arrange(Condition, Treatment)

malic.control2.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk2.controls)
summary(malic.control2.aov) # not sigificant between autoclaved and inoculated controls

# Week 4
wk4.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_4") %>% 
  arrange(Condition, Treatment)

malic.control4.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk4.controls)
summary(malic.control4.aov) # not sigificant between autoclaved and inoculated controls

# Week 6
wk6.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_6") %>% 
  arrange(Condition, Treatment)

malic.control6.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk6.controls)
summary(malic.control6.aov) # not sigificant between autoclaved and inoculated controls

# Week 8
wk8.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_8") %>% 
  arrange(Condition, Treatment)

malic.control8.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk8.controls)
summary(malic.control8.aov) # not sigificant between autoclaved and inoculated controls

# removing Control Mock & fixing 'Null isolates'
clusia.malic <- clusia.malic %>% 
  filter(Treatment != "Control Mock")

clusia.malic$Treatment[clusia.malic$Treatment == "Null Isolates"] <- "Nonfunctional Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "Null_Isolates"] <- "Nonfunctional Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "All_Isolates"] <- "All Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "Drought_Isolates"] <- "Drought Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "Phosphorus_Isolates"] <- "Phosphorus Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "Drought"] <- "Drought Isolates"

# arranging by Week, Water, and Treatment
clusia.malic <- clusia.malic %>% 
  arrange(Week, Condition, Treatment)
View(clusia.malic)
```


### Mean, SD, Std.Error
```{r}
# subsetting to Wk 0 ,4, 8
clusia.malic <- clusia.malic %>% 
  filter(Week == "Wk_0" | Week == "Wk_4" | Week == "Wk_8")

cond_malic <- ggplot(data = clusia.malic, aes(x = Condition, y = MalicAverage)) + geom_boxplot() + facet_grid(. ~ Week)+ mytheme + ylab(" Malic Acid") + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 90))

pdf("cond_malic.pdf")
plot(cond_malic)
dev.off()

cond_treat_malic <- ggplot(data = clusia.malic, aes(x = Treatment, y = MalicAverage, fill = Condition)) + geom_boxplot() + facet_grid(. ~ Week)+ mytheme + ylab(" Malic Acid") + theme(axis.title.x = element_blank()) + mytheme + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(axis.text.x = element_text(angle = 90)) + xlab("Constructed Community")

pdf("cond_treat_malic.pdf")
plot(cond_treat_malic)
dev.off()

# mean
malic.sum <- clusia.malic %>% 
  group_by(Week, Condition) %>% 
  summarise(n = n(),
            mean_malic = mean(MalicAverage, na.rm = TRUE),
            sd_malic = sd(MalicAverage, na.rm = TRUE),
            se = sd(MalicAverage, na.rm = TRUE)/sqrt(n()))

mean_malic <- ggplot(data = malic.sum, aes(x = Condition, y = mean_malic, fill = Week)) + geom_bar(stat = "identity", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = mean_malic-se, ymax = mean_malic+se), width=0.2, position = position_dodge(0.9)) + mytheme + ylab("Mean Malic Acid") + theme(axis.title.x = element_blank()) + scale_fill_manual(values = wes_palette(n = 5, name = "Royal2"))

pdf("mean_malic.pdf")
plot(mean_malic)
dev.off()

malic.sum2 <- clusia.malic %>% 
  group_by(Week, Condition, Treatment) %>% 
  summarise(n = n(),
            mean_malic = mean(MalicAverage, na.rm = TRUE),
            sd_malic = sd(MalicAverage, na.rm = TRUE),
            se = sd(MalicAverage, na.rm = TRUE)/sqrt(n()))

mean_malic2 <- ggplot(data = malic.sum2, aes(x = Treatment, y = mean_malic, fill = Condition)) + geom_bar(stat = "identity", position = position_dodge(0.9), colour = "black") + geom_errorbar(aes(ymin = mean_malic-se, ymax = mean_malic+se), width=0.2, position = position_dodge(0.9)) + facet_grid(. ~ Week) + mytheme + ylab("Mean Malic Acid") + xlab("Constructed Community") + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1))

pdf("mean_malic2.pdf")
plot(mean_malic2)
dev.off()

```

### Malic Acid ANOVAs
#### Week 0
```{r Malic Acid Week 0}

# subsetting Week 0
malic.wk0 <- clusia.malic %>% 
  filter(Week == "Wk_0")

# density histogram
ggplot(data = malic.wk0, aes(x = MalicAverage)) + geom_histogram(binwidth = 25, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
malic.wk0.mu <- malic.wk0%>% 
  group_by(Condition) %>% 
  summarise(mean = mean(MalicAverage, na.rm = TRUE))

ggplot(data = malic.wk0, aes(x = MalicAverage, fill = Condition)) + geom_histogram(binwidth = 25, position = "identity", alpha = 0.5) + geom_vline(data = malic.wk0.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Malic Acid") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
malic.wk0.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk0)
summary(malic.wk0.aov) # not sigificant between treatment

# testing homogeneity of variances
plot(malic.wk0.aov, 1)
leveneTest(MalicAverage ~ Condition*Treatment, data = malic.wk0) # p > 0.05 means no violation of homogeneity of varaince

# normality test
plot(malic.wk0.aov, 2)
malic.wk0.residuals <- residuals(object = malic.wk0.aov)
shapiro.test(x = malic.wk0.residuals) # p > 0.05 means normal data 

ggqqplot(malic.wk0$MalicAverage)
shapiro.test(malic.wk0$MalicAverage)
```

#### Week 2
```{r Malic Acid Week 2}
malic.wk2 <- clusia.malic %>% 
  filter(Week == "Wk_2")

malic.wk2.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk2)
summary(malic.wk2.aov)
```

#### Week 4
```{r Malic Acid Week 4}
# subset for Week 4
malic.wk4 <- clusia.malic %>% 
  filter(Week == "Wk_4")

# density histogram
ggplot(data = malic.wk4, aes(x = MalicAverage)) + geom_histogram(binwidth = 50, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
malic.wk4.mu <- malic.wk4%>% 
  group_by(Condition) %>% 
  summarise(mean = mean(MalicAverage, na.rm = TRUE))

ggplot(data = malic.wk4, aes(x = MalicAverage, fill = Condition)) + geom_histogram(binwidth = 50, position = "identity", alpha = 0.5) + geom_vline(data = malic.wk4.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Malic Acid") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
malic.wk4.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk4)
summary(malic.wk4.aov)

# testing homogeneity of variances
plot(malic.wk4.aov, 1)
leveneTest(MalicAverage ~ Condition*Treatment, data = malic.wk4) # p > 0.05 means no violation of homogeneity of varaince

# normality test
plot(malic.wk4.aov, 2)
malic.wk4.residuals <- residuals(object = malic.wk4.aov)
shapiro.test(x = malic.wk4.residuals) # p > 0.05 means normal data

ggqqplot(malic.wk4$MalicAverage)
shapiro.test(malic.wk4$MalicAverage)
```

#### Week 6
```{r Malic Acid Week 6}
malic.wk6 <- clusia.malic %>% 
  filter(Week == "Wk_6")

malic.wk6.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk6)
summary(malic.wk6.aov) # sigificant drought effect
```

#### Week 8
```{r Malic Acid Week 8}
# subsetting for Week 8 
malic.wk8 <- clusia.malic %>% 
  filter(Week == "Wk_8")

# density histogram
ggplot(data = malic.wk8, aes(x = MalicAverage)) + geom_histogram(binwidth = 80, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
malic.wk8.mu <- malic.wk8%>% 
  group_by(Condition) %>% 
  summarise(mean = mean(MalicAverage, na.rm = TRUE))

ggplot(data = malic.wk8, aes(x = MalicAverage, fill = Condition)) + geom_histogram(binwidth = 80, position = "identity", alpha = 0.5) + geom_vline(data = malic.wk4.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Malic Acid") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
malic.wk8.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk8)
summary(malic.wk8.aov) # significant drought effect and microbial effect
TukeyHSD(malic.wk8.aov)

# testing homogeneity of variances
plot(malic.wk8.aov, 1)
leveneTest(MalicAverage ~ Condition*Treatment, data = malic.wk8) # p > 0.05 means no violation of homogeneity of varaince

# normality test
plot(malic.wk8.aov, 2)
malic.wk8.residuals <- residuals(object = malic.wk8.aov)
shapiro.test(x = malic.wk8.residuals) # p > 0.05 means normal data

ggqqplot(malic.wk8$MalicAverage)
shapiro.test(malic.wk8$MalicAverage)
```

```{r Malic Acid Week 8 Outliers}

# identifying outliers
wk8.mod <- lm(MalicAverage ~ Condition, data = malic.wk8)
cooksd.wk8 <- cooks.distance(wk8.mod)

plot(cooksd.wk8, pch = "*", cex = 2, main = "Influential Observations in Wk 8 Malic Acid")
abline(h = 4*mean(cooksd.wk8, na.rm = T), col = "red")
text(x=1: length(cooksd.wk8) + 1, y= cooksd.wk8, labels = ifelse(cooksd.wk8>4*mean(cooksd.wk8, na.rm = T), names(cooksd.wk8), ""), col = "red")

wk8.malic.out <- as.numeric(names(cooksd.wk8)[(cooksd.wk8 > 4*mean(cooksd.wk8, na.rm = T))])
head(biomass[wk8.malic.out, ])

# removing outliers and testing impact
malic.wk8 <- malic.wk8[-c(24), ]

ggqqplot(malic.wk8$MalicAverage)
shapiro.test(malic.wk8$MalicAverage)
```

```{r Malic Acid Boxplot}

clusia.boxplot <- ggplot(data = clusia.malic, aes(x = Treatment, y = MalicAverage, fill = Condition)) + geom_boxplot() + geom_point(aes(fill = Condition), size = 2, shape = 21, position = position_jitterdodge()) + facet_grid(. ~ Week) 

clusia.boxplot <- clusia.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.095, 0.9))

clusia.boxplot <- clusia.boxplot + ylab(expression(Malic~Acid~Concentration~(mu~mol~H~g^{-1})))

pdf("MalicAcid_Boxplot.pdf")
plot(clusia.boxplot)
dev.off()
```

At Week 0, both well-watered and drought plants show no difference in malic acid concentrations as expected. However, as the drought trial progresses, well-watered plants and drought plants begin to diverge significantly at Week 2 (p-value < 0.001). Higher amounts of malic acid in well-watered plants indicate higher CAM activity, which is in contrast with hypotheses that CAM activity would be highest in drought plants due to experiencing drought stress. Furthermore, there was no significant effect of microbial community until the last week (p- value < 0.05) with no interaction term, suggesting that availability of water is still the dominant driver of malic acid concentration. Tukeys HSD results indicate that although the differences in microbial communities are different, that these differences are occuring between well-watered microbial communities versus droughted microbial communities, verifying that the water availability is driving differences between plants and not the composition of the the microbial communities themselves. 

## Lipid Peroxidation Assay
```{r Importing Lipid Peroxidation Data}
clusia.lipid <- read.csv("~/Documents/Git/clusia_droughtexperiment/LipidPeroxidation.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
```

### Lipid Peroxidation Controls
```{r Lipid Peroxidation Controls}
# Week 0
wk0.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_0") %>% 
  arrange(Condition, Treatment)

lipid.control0.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk0.controls)
summary(lipid.control0.aov) # not sigificant between autoclaved and inoculated controls

# Week 2
wk2.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_2") %>% 
  arrange(Condition, Treatment)

lipid.control2.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk2.controls)
summary(lipid.control2.aov) # not sigificant between autoclaved and inoculated controls

# Week 4
wk4.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_4") %>% 
  arrange(Condition, Treatment)

lipid.control4.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk4.controls)
summary(lipid.control4.aov) # not sigificant between autoclaved and inoculated controls

# Week 6
wk6.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_6") %>% 
  arrange(Condition, Treatment)

lipid.control6.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk6.controls)
summary(lipid.control6.aov) # not sigificant between autoclaved and inoculated controls

# Week 8
wk8.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_8") %>% 
  arrange(Condition, Treatment)

lipid.control8.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk8.controls)
summary(lipid.control8.aov) # not sigificant between autoclaved and inoculated controls

# removing Control Mock
clusia.lipid <- clusia.lipid %>% 
  filter(Treatment != "Control Mock")

# arranging by Week, Water, and Treatment
clusia.lipid <- clusia.lipid %>% 
  arrange(Week, Condition, Treatment)
```

### Mean, SD, Std. Error
```{r}
# selecting Week 0 , 4, 8
clusia.lipid <- clusia.lipid %>% 
  filter(Week == "Wk_0" | Week == "Wk_4" | Week == "Wk_8")

cond.lipid <- ggplot(data = clusia.lipid, aes(x = Condition, y = LipidPerox)) + geom_boxplot() + facet_grid(.~Week) + mytheme + theme(axis.title.x = element_blank()) + ylab("Lipid Peroxidation") + scale_y_continuous(limits = c(0, 200))

pdf("cond_lipid.pdf")
plot(cond.lipid)
dev.off()

cond.treat.lipid <- ggplot(data = clusia.lipid, aes(x = Treatment, y = LipidPerox, fill = Condition)) + geom_boxplot() + facet_grid(.~Week) + mytheme + theme(axis.title.x = element_blank()) + ylab("Lipid Peroxidation") + scale_y_continuous(limits = c(0, 200)) + theme(axis.text.x = element_text(angle = 90)) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought"))

pdf("cond_treat_lipid.pdf")
plot(cond.treat.lipid)
dev.off()

lipid.sum <- clusia.lipid %>% 
  group_by(Week, Condition) %>% 
  summarise(n = n(),
            mean_lipid = mean(LipidPerox, na.rm = TRUE),
            sd_lipid = sd(LipidPerox, na.rm = TRUE),
            se = sd(LipidPerox, na.rm = TRUE)/sqrt(n()))

mean_lipid <- ggplot(data = lipid.sum , aes(x = Condition, y = mean_lipid)) + geom_bar(stat = "identity", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = mean_lipid-se, ymax =mean_lipid+se), width=0.2, position = position_dodge(0.9)) + facet_grid(. ~ Week) + mytheme + ylab("Mean Lipid Peroxidation") + theme(axis.title.x = element_blank()) 

pdf("mean_lipid.pdf")
plot(mean_lipid)
dev.off()

lipid.sum2 <- clusia.lipid %>% 
  group_by(Week, Condition, Treatment) %>% 
  summarise(n = n(),
            mean_lipid = mean(LipidPerox, na.rm = TRUE),
            sd_lipid = sd(LipidPerox, na.rm = TRUE),
            se = sd(LipidPerox, na.rm = TRUE)/sqrt(n()))

mean_lipid2 <- ggplot(data = lipid.sum2, aes(x = Treatment, y = mean_lipid, fill = Condition)) + geom_bar(stat = "identity", position = position_dodge(0.9), colour = "black") + geom_errorbar(aes(ymin = mean_lipid-se, ymax =mean_lipid+se), width=0.2, position = position_dodge(0.9)) + facet_grid(. ~ Week) + mytheme + ylab("Mean Lipid Peroxidation") + theme(axis.title.x = element_blank()) + scale_y_continuous(limits = c(0, 200)) + theme(axis.text.x = element_text(angle = 90)) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought"))

pdf("mean_lipid2.pdf")
plot(mean_lipid2)
dev.off()
```

### Lipid Peroxidation ANOVAs
#### Week 0
```{r Lipid Perox Week 0}
# Week 0
lipid.wk0 <- clusia.lipid %>% 
  filter(Week == "Wk_0")

# density histogram
ggplot(data = lipid.wk0, aes(x = LipidPerox)) + geom_histogram(binwidth = 5, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
lipid.wk0.mu <- lipid.wk0 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(LipidPerox, na.rm = TRUE))

ggplot(data = lipid.wk0, aes(x = LipidPerox, fill = Condition)) + geom_histogram(binwidth = 5, position = "identity", alpha = 0.5) + geom_vline(data = lipid.wk0.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Lipid Peroxidation") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
lipid.wk0.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk0)
summary(lipid.wk0.aov) 

# testing homogeneity of variances
plot(lipid.wk0.aov, 1)
leveneTest(LipidPerox ~ Condition*Treatment, data = lipid.wk0) # p > 0.05 means no violation of homogeneity of varaince

# normality test
plot(lipid.wk0.aov, 2)
lipid.wk0.residuals <- residuals(object = lipid.wk0.aov)
shapiro.test(x = lipid.wk0.residuals) # p < 0.05 means normal data

ggqqplot(lipid.wk0$LipidPerox)
shapiro.test(lipid.wk0$LipidPerox)
```

```{r Lipid Perox Week 0 Outliers}
# identifying outliers
lipid.wk0.mod <- lm(LipidPerox ~ Condition, data = lipid.wk0)
cooksd.wk0 <- cooks.distance(lipid.wk0.mod)

plot(cooksd.wk0, pch = "*", cex = 2, main = "Influential Observations in Wk 0 Lipid Peroxidation")
abline(h = 4*mean(cooksd.wk0, na.rm = T), col = "red")
text(x=1: length(cooksd.wk0) + 1, y= cooksd.wk0, labels = ifelse(cooksd.wk0>4*mean(cooksd.wk0, na.rm = T), names(cooksd.wk0), ""), col = "red")

wk0.lipid.out <- as.numeric(names(cooksd.wk0)[(cooksd.wk0 > 4*mean(cooksd.wk0, na.rm = T))])
head(clusia.lipid[wk0.lipid.out, ])

# removing outliers and testing impact
lipid.wk0 <- lipid.wk0[-c(5), ]

ggqqplot(lipid.wk0$LipidPerox)
shapiro.test(lipid.wk0$LipidPerox)
```

#### Week 2
```{r Lipid Perox Week 2}
# Week 2
lipid.wk2 <- clusia.lipid %>% 
  filter(Week == "Wk_2")

lipid.wk2.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk2)
summary(lipid.wk2.aov)
```

#### Week 4
```{r Lipid Perox Week 4}
# Week 4
lipid.wk4 <- clusia.lipid %>% 
  filter(Week == "Wk_4")

# density histogram
ggplot(data = lipid.wk4, aes(x = LipidPerox)) + geom_histogram(binwidth = 8, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
lipid.wk4.mu <- lipid.wk4 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(LipidPerox, na.rm = TRUE))

ggplot(data = lipid.wk4, aes(x = LipidPerox, fill = Condition)) + geom_histogram(binwidth = 8, position = "identity", alpha = 0.5) + geom_vline(data = lipid.wk4.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Lipid Peroxidation") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
lipid.wk4.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk4)
summary(lipid.wk4.aov) 

# testing homogeneity of variances
plot(lipid.wk4.aov, 1)
leveneTest(LipidPerox ~ Condition*Treatment, data = lipid.wk4) 

# normality test
plot(lipid.wk4.aov, 2)
lipid.wk4.residuals <- residuals(object = lipid.wk4.aov)
shapiro.test(x = lipid.wk4.residuals) 

ggqqplot(lipid.wk4$LipidPerox)
shapiro.test(lipid.wk4$LipidPerox)
```

#### Week 6
```{r Lipid Perox Week 6}
# Week 6
lipid.wk6 <- clusia.lipid %>% 
  filter(Week == "Wk_6")

lipid.wk6.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk6)
summary(lipid.wk6.aov)
```

#### Week 8
```{r Lipid Perox Week 8}
lipid.wk8 <- clusia.lipid %>% 
  filter(Week == "Wk_8")

# density histogram
ggplot(data = lipid.wk8, aes(x = LipidPerox)) + geom_histogram(binwidth = 10, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
lipid.wk8.mu <- lipid.wk8 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(LipidPerox, na.rm = TRUE))

ggplot(data = lipid.wk8, aes(x = LipidPerox, fill = Condition)) + geom_histogram(binwidth = 10, position = "identity", alpha = 0.5) + geom_vline(data = lipid.wk8.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Lipid Peroxidation") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
lipid.wk8.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk8)
summary(lipid.wk8.aov)
TukeyHSD(lipid.wk8.aov)

# testing homogeneity of variances
plot(lipid.wk8.aov, 1)
leveneTest(LipidPerox ~ Condition*Treatment, data = lipid.wk8) # p > 0.05 means no violation of homogeneity of varaince

# normality test
plot(lipid.wk8.aov, 2)
lipid.wk8.residuals <- residuals(object = lipid.wk8.aov)
shapiro.test(x = lipid.wk8.residuals)
```


```{r Lipid Peroxidation Boxplot}
lipid.boxplot <- ggplot(data = clusia.lipid, aes(x = Treatment, y = LipidPerox, fill = Condition)) + geom_boxplot() + geom_point(aes(fill = Condition), size = 2, shape = 21, position = position_jitterdodge()) + facet_grid(. ~ Week) 

lipid.boxplot <- lipid.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.1, 0.8)) + ylab(expression(Lipid~Peroxidation~(nmol~MDA~g^{-1})))

lipid.boxplot <- lipid.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.1, 0.8))


pdf("LipidPerox_Boxplot.pdf")
plot(lipid.boxplot)
dev.off()
```


Lipd peroxidation did not differ signifcantly between well-watered plants and drought plants until the final week of the experiment. Overall, plants inoculated with all beneficial isolates (All Isolates) differed from control plants (Control), plants that received autoclaved bacteria (Control Mock), and plants that received isolates with no measured function (Nonfunctional) (p-value < 0.05). The greatest differences in lipid peroxidation occured between well-watered plants and drought plants, indepent of microbial community. Although there is a significant microbial effect (p-value < 0.01), there is no interaction term suggesting that lipid peroxidation in drought conditions is not tied to microbial community composition despite the general differences between plants incolated with beneficial isolates and those of the control.  


## Proline Assay
```{r Importing Proline Data}
clusia.proline <- read.csv("~/Documents/Git/clusia_droughtexperiment/Proline.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
```

### Proline Controls
```{r Checking Controls - Proline}
# Week 0
wk0.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_0") %>% 
  arrange(Condition, Treatment)

proline.control0.aov <- aov(Proline ~ Condition * Treatment, data = wk0.controls)
summary(proline.control0.aov) # not sigificant between autoclaved and inoculated controls

# Week 2
wk2.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_2") %>% 
  arrange(Condition, Treatment)

proline.control2.aov <- aov(Proline ~ Condition * Treatment, data = wk2.controls)
summary(proline.control2.aov) # not sigificant between autoclaved and inoculated controls

# Week 4
wk4.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_4") %>% 
  arrange(Condition, Treatment)

proline.control4.aov <- aov(Proline ~ Condition * Treatment, data = wk4.controls)
summary(proline.control4.aov) # significant interaction term + significant at < 0.1 for drought and microbial effect

# Week 6
wk6.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_6") %>% 
  arrange(Condition, Treatment)

proline.control6.aov <- aov(Proline ~ Condition * Treatment, data = wk6.controls)
summary(proline.control6.aov) # significant drought effect

# Week 8
wk8.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_8") %>% 
  arrange(Condition, Treatment)

proline.control8.aov <- aov(Proline ~ Condition * Treatment, data = wk8.controls)
summary(proline.control8.aov) # significant drought effect

# removing Control Mock & fixing 'Null isolates'
clusia.proline <- clusia.proline %>% 
  filter(Treatment != "Control Mock")

# arranging by Week, Water, and Treatment
clusia.proline <- clusia.proline %>% 
  arrange(Week, Condition, Treatment)
View(clusia.proline)
```

### Mean, SD, Std. Error
```{r}
clusia.proline <- clusia.proline %>% 
  filter(Week == "Wk_0" | Week == "Wk_4" | Week == "Wk_8")

cond.proline <- ggplot(data = clusia.proline, aes(x = Condition, y = Proline)) + geom_boxplot() + facet_grid(. ~ Week) + mytheme + theme(axis.title.x = element_blank()) + scale_y_continuous(limits = c(0, 50)) 

pdf("cond_proline.pdf")
plot(cond.proline)
dev.off()

cond.treat.proline <- ggplot(data = clusia.proline, aes(x = Treatment, y = Proline, fill = Condition)) + geom_boxplot() + facet_grid(. ~ Week) + mytheme + theme(axis.title.x = element_blank()) + scale_y_continuous(limits = c(0, 50)) + theme(axis.text.x = element_text(angle = 90)) + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought"))

pdf("cond_treat_proline.pdf")
plot(cond.treat.proline)
dev.off()

proline.sum <- clusia.proline %>% 
  group_by(Week, Condition) %>% 
  summarise(n = n(),
            mean_proline = mean(Proline, na.rm = TRUE),
            sd_proline = sd(Proline, na.rm = TRUE),
            se = sd(Proline, na.rm = TRUE)/sqrt(n()))
View(proline.sum)

mean_proline <- ggplot(data = proline.sum, aes(x = Condition, y = mean_proline)) + geom_bar(stat = "identity", color = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = mean_proline-sd_proline, ymax = mean_proline+sd_proline), width = 0.2, position = position_dodge(0.9)) + facet_grid(. ~ Week) + mytheme + theme(axis.title.x = element_blank()) + ylab("Mean Proline")

pdf("mean_proline.pdf")
plot(mean_proline)
dev.off()

proline.sum2 <- clusia.proline %>% 
  group_by(Week, Condition, Treatment) %>% 
  summarise(n = n(),
            mean_proline = mean(Proline, na.rm = TRUE),
            sd_proline = sd(Proline, na.rm = TRUE),
            se = sd(Proline, na.rm = TRUE)/sqrt(n()))
View(proline.sum2)

mean_proline2 <- ggplot(data = proline.sum2, aes(x = Treatment, y = mean_proline, fill = Condition)) + geom_bar(stat = "identity", color = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = mean_proline-sd_proline, ymax = mean_proline+sd_proline), width = 0.2, position = position_dodge(0.9)) + facet_grid(. ~ Week) + mytheme + theme(axis.title.x = element_blank()) + ylab("Mean Proline") + scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + scale_y_continuous(limits = c(0, 50)) + theme(axis.text.x = element_text(angle = 90)) 

pdf("mean_proline2.pdf")
plot(mean_proline2)
dev.off()
```

### Proline ANOVAs
#### Week 0
```{r Proline Week 0}
# Week 0
proline.wk0 <- clusia.proline %>% 
  filter(Week == "Wk_0")

# density histogram
ggplot(data = proline.wk0, aes(x = Proline)) + geom_histogram(binwidth = 2, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
proline.wk0.mu <- proline.wk0 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(Proline, na.rm = TRUE))

ggplot(data = proline.wk0, aes(x = Proline, fill = Condition)) + geom_histogram(binwidth = 2, position = "identity", alpha = 0.5) + geom_vline(data = proline.wk0.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Proline") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
proline.wk0.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk0)
summary(proline.wk0.aov) 

# testing homogeneity of variances
plot(proline.wk0.aov, 1)
leveneTest(Proline ~ Condition*Treatment, data = proline.wk0) 

# normality test
plot(proline.wk0.aov, 2)
proline.wk0.residuals <- residuals(object = proline.wk0.aov)
shapiro.test(x = proline.wk0.residuals)
```

#### Week 2
```{r Proline Week 2}
# Week 2
proline.wk2 <- clusia.proline %>% 
  filter(Week == "Wk_2")

# ANOVA
proline.wk2.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk2)
summary(proline.wk2.aov) # significant drought effect (<0.1) and interaction term (< 0.05)
```

#### Week 4
```{r Proline Week 4}
# Week 4
proline.wk4 <- clusia.proline %>% 
  filter(Week == "Wk_4")

# density histogram
ggplot(data = proline.wk4, aes(x = Proline)) + geom_histogram(binwidth = 2.5, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
proline.wk4.mu <- proline.wk4 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(Proline, na.rm = TRUE))

ggplot(data = proline.wk4, aes(x = Proline, fill = Condition)) + geom_histogram(binwidth = 2.5, position = "identity", alpha = 0.5) + geom_vline(data = proline.wk4.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Proline") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
proline.wk4.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk4)
summary(proline.wk4.aov) # significant drought effect

# testing homogeneity of variances
plot(proline.wk4.aov, 1)
leveneTest(Proline ~ Condition*Treatment, data = proline.wk4)

# normality test
plot(proline.wk4.aov, 2)
proline.wk4.residuals <- residuals(object = proline.wk4.aov)
shapiro.test(x = proline.wk4.residuals)
```

#### Week 6
```{r Proline Week 6}
proline.wk6 <- clusia.proline %>% 
  filter(Week == "Wk_6")

proline.wk6.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk6)
summary(proline.wk6.aov)  # significant drought effect (<0.001), microbial (<0.1), interaction (<0.1)

TukeyHSD(proline.wk6.aov)
```

#### Week 8
```{r Proline Week 8}
# Week 8
proline.wk8 <- clusia.proline %>% 
  filter(Week == "Wk_8")

# density histogram
ggplot(data = proline.wk8, aes(x = Proline)) + geom_histogram(binwidth = 4.5, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
proline.wk8.mu <- proline.wk8 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(Proline, na.rm = TRUE))

ggplot(data = proline.wk8, aes(x = Proline, fill = Condition)) + geom_histogram(binwidth = 4.5, position = "identity", alpha = 0.5) + geom_vline(data = proline.wk8.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Proline") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
proline.wk8.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk8)
summary(proline.wk8.aov) # significant drought effect (<0.001) and microbial effect (<0.1)

# testing homogeneity of variances
plot(proline.wk8.aov, 1)
leveneTest(Proline ~ Condition*Treatment, data = proline.wk8) # p > 0.05 means no violation of homogeneity of varaince

# normality test
plot(proline.wk8.aov, 2)
proline.wk8.residuals <- residuals(object = proline.wk8.aov)  # p > 0.05 means no violation of homogeneity of varaince
shapiro.test(x = proline.wk8.residuals)
```

```{r Proline Boxplot}

proline.boxplot <- ggplot(data = clusia.proline, aes(x = Treatment, y = Proline, fill = Condition)) + geom_boxplot() + geom_point(aes(fill = Condition), size = 2, shape = 21, position = position_jitterdodge()) + facet_grid(. ~ Week) 

proline.boxplot <- proline.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.09, 0.85))

pdf("Proline_Boxplot.pdf")
plot(proline.boxplot)
dev.off()

```

Water is predominantly the determinant of proline concentration, though not until Week 4. Unlike malic acid and lipid peroxidation, there is a slight influence of microbial community on proline in Week 6 and Week 8 (p-value < 0.1), though Tukeys HSD shows that these differences are the result of differences between well-watered communities and droughted communities. Therefore, the significant interaction term is not an indication that plants containing each constructed communities respond differently within the drought treatment. Well-watered plants have significantly lower amounts of proline than drought plants at Week 4 (p-value < 0.05), with the gap between the two widening over time. This is consistent with proline being a stress metabolite that increases in response to drought stress.


## Osmolality
```{r Dataset}
osmo <- read.csv("~/Documents/Git/clusia_droughtexperiment/Osmolality.csv", header = TRUE, stringsAsFactors = TRUE)
osmo <- osmo %>% 
  arrange(Week, Condition, Treatment)
```


### Controls
```{r Osmo Controls}
# Week 0
wk0.cont <- osmo %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_0")

wk0.cont.aov <- aov(Osmolality ~ Condition * Treatment, data = wk0.cont)
summary(wk0.cont.aov) # no significant differences between control mock and control

# Week 2
wk2.cont <- osmo %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_2")

wk2.cont.aov <- aov(Osmolality ~ Condition * Treatment, data = wk2.cont)
summary(wk2.cont.aov) # no significant differences between control mock and control

# Week 4
wk4.cont <- osmo %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_4")

wk4.cont.aov <- aov(Osmolality ~ Condition * Treatment, data = wk4.cont)
summary(wk4.cont.aov) # no significant differences between control mock and control

# Week 6
wk6.cont <- osmo %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_6")

wk6.cont.aov <- aov(Osmolality ~ Condition * Treatment, data = wk6.cont)
summary(wk6.cont.aov) # no significant differences between control mock and control

# Week 8 
wk8.cont <- osmo %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_8")

wk8.cont.aov <- aov(Osmolality ~ Condition * Treatment, data = wk8.cont)
summary(wk8.cont.aov) # no significant differences between control mock and control

# removing Control Mocks
osmo <- osmo %>% 
  filter(Treatment != "Control Mock")
```

### Mean, SD, SE
```{r}
osmo$Week[osmo$Week == "WK_8"] <- "Wk_8" # fixing error

# filtering out certain weeks
osmo <- osmo %>% 
  filter(Week == "Wk_0" | Week == "Wk_4" | Week == "Wk_8")
View(osmo)

ggplot(data = osmo, aes(x = Condition, y = Osmolality)) + geom_boxplot() + facet_grid(. ~ Week) + mytheme + theme(axis.title.x = element_blank()) + scale_y_continuous(limits = c(0, 800))

# mean
osmo.sum <- osmo %>% 
  group_by(Week, Condition) %>% 
  summarise(n = n(),
            mean = mean(Osmolality, na.rm = TRUE),
            sd = sd(Osmolality, na.rm = TRUE),
            se = sd(Osmolality, na.rm = TRUE)/sqrt(n()))
View(osmo.sum)

mean_osmo <- ggplot(data = osmo.sum, aes(x = Condition, y = mean)) + geom_bar(stat = "identity", colour = "black", position = position_dodge(0.9)) + facet_grid(.~Week) + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), width = 0.2, position = position_dodge(0.9)) + mytheme + theme(axis.title.x = element_blank()) + ylab("Mean Osmolality")

pdf("mean_osmo.pdf")
plot(mean_osmo)
dev.off()

osmo.sum2 <- osmo %>% 
  group_by(Week, Condition, Treatment) %>% 
  summarise(n = n(),
            mean = mean(Osmolality, na.rm = TRUE),
            sd = sd(Osmolality, na.rm = TRUE),
            se = sd(Osmolality, na.rm = TRUE)/sqrt(n()))
View(osmo.sum2)

mean.osmo2 <- ggplot(data = osmo.sum2, aes(x = Treatment, y = mean, fill = Condition)) + geom_bar(stat = "identity", color = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), width = 0.2, position = position_dodge(0.9)) + facet_grid(. ~ Week) + mytheme +  scale_fill_manual(values=c("#FFFFFF", "#CCCCCC"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(axis.text.x = element_text(angle = 90)) + xlab("Constructed Community") + ylab("Mean Osmolality")

pdf("mean_osmo2.pdf")
plot(mean.osmo2)
dev.off()

```
### ANOVAs
#### Week 0
```{r Osmolality Week 0}
# Week 0
osmo.wk0 <- osmo %>% 
  filter(Week == "Wk_0")

# density histogram
ggplot(data = osmo.wk0, aes(x = Osmolality)) + geom_histogram(binwidth = 30, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
osmo.wk0.mu <- osmo.wk0 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(Osmolality, na.rm = TRUE))

ggplot(data = osmo.wk0, aes(x = Osmolality, fill = Condition)) + geom_histogram(binwidth = 30, position = "identity", alpha = 0.5) + geom_vline(data = osmo.wk0.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Osmolality") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
osmo.wk0.aov <- aov(Osmolality ~ Condition * Treatment, data = osmo.wk0)
summary(osmo.wk0.aov)

# testing homogeneity of variances
plot(osmo.wk0.aov, 1)
leveneTest(Osmolality ~ Condition*Treatment, data = osmo.wk0) # p > 0.05 means no violation of homogeneity of varaince

# normality test
plot(osmo.wk0.aov, 2)
osmo.wk0.residuals <- residuals(object = osmo.wk0.aov)  # p > 0.05 means no violation of homogeneity of varaince
shapiro.test(x = osmo.wk0.residuals)
```

#### Week 2
```{r Osmolality Week 2}
# Week 2 
wk2 <- osmo %>% 
  filter(Week == "Wk_2")

# ANOVA
wk2.aov <- aov(Osmolality ~ Condition * Treatment, data = wk2)
summary(wk2.aov)
```

#### Week 4
```{r Osmolality Week 4}
# Week 4
osmo.wk4 <- osmo %>% 
  filter(Week == "Wk_4")

# density histogram
ggplot(data = osmo.wk4, aes(x = Osmolality)) + geom_histogram(binwidth = 52, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
osmo.wk4.mu <- osmo.wk4 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(Osmolality, na.rm = TRUE))

ggplot(data = osmo.wk4, aes(x = Osmolality, fill = Condition)) + geom_histogram(binwidth = 52, position = "identity", alpha = 0.5) + geom_vline(data = osmo.wk4.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Osmolality") + ylab("Count") + theme(legend.position = c(0.9, 0.9))
osmo.wk4.aov <- aov(Osmolality ~ Condition * Treatment, data = osmo.wk4)
summary(osmo.wk4.aov) # significant drought, microbial, and interaction term
TukeyHSD(osmo.wk4.aov)

# ANOVA
osmo.wk4.aov <- aov(Osmolality ~ Condition * Treatment, data = osmo.wk4)
summary(osmo.wk4.aov) # significant drought, microbial, and interaction term
TukeyHSD(osmo.wk4.aov)

# testing homogeneity of variances
plot(osmo.wk4.aov, 1)
leveneTest(Osmolality ~ Condition*Treatment, data = osmo.wk4)

# normality test
plot(osmo.wk4.aov, 2)
osmo.wk4.residuals <- residuals(object = osmo.wk4.aov)
shapiro.test(x = osmo.wk4.residuals)
```

#### Week 6
```{r Osmolality Week 6}
# Week 6
wk6 <- osmo %>% 
  filter(Week == "Wk_6")

# ANOVA
wk6.aov <- aov(Osmolality ~ Condition * Treatment, data = wk6)
summary(wk6.aov) 
```

#### Week 8
```{r Osmolality Week 8}
# Week 8
osmo.wk8 <- osmo %>% 
  filter(Week == "Wk_8")

# density histogram
ggplot(data = osmo.wk8, aes(x = Osmolality)) + geom_histogram(binwidth = 110, aes(y =..density..), colour = "black", fill = "white") + geom_density(alpha = 0.2, fill = "#FF6666") 

# by water treatment
osmo.wk8.mu <- osmo.wk8 %>% 
  group_by(Condition) %>% 
  summarise(mean = mean(Osmolality, na.rm = TRUE))

ggplot(data = osmo.wk8, aes(x = Osmolality, fill = Condition)) + geom_histogram(binwidth = 110, position = "identity", alpha = 0.5) + geom_vline(data = osmo.wk8.mu, aes(xintercept=mean, color=Condition), linetype="dashed") + scale_color_manual(values=c("indianred3", "cadetblue3")) + theme_classic() + xlab("Osmolality") + ylab("Count") + theme(legend.position = c(0.9, 0.9))

# ANOVA
osmo.wk8.aov <- aov(Osmolality ~ Condition * Treatment, data = osmo.wk8)
summary(osmo.wk8.aov)

# testing homogeneity of variances
plot(osmo.wk8.aov, 1)
leveneTest(Osmolality ~ Condition*Treatment, data = osmo.wk8) # p < 0.05 means violation of homogeneity of varaince

# normality test
plot(osmo.wk8.aov, 2)
osmo.wk8.residuals <- residuals(object = osmo.wk8.aov)  # p > 0.05 means no violation of homogeneity of varaince
shapiro.test(x = osmo.wk8.residuals)
```

