---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    df_print: paged
    code_folding: hide
    toc: true
    toc_float: true
---

<<<<<<< HEAD
# Introduction
# Methods
# Biomass Measurements
# Physiology Measurements
##  Malic Acid Titrations
```{r Importing Malic Acid Data}
library(tidyverse)
clusia.malic <- read.csv("~/Documents/LabStats/Clusia/MalicAcid.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
```

### Malic Acid Controls
=======
# Malic Acid Titrations
```{r Importing Malic Acid Data}
library(tidyverse)
clusia.malic <- read.csv("~/Documents/Git/clusia_droughtexperiment/MalicAcid.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
View(clusia.malic)
str(clusia.malic)
```

>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
```{r Malic Acid Controls}
# Week 0
wk0.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_0") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk0.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.control0.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk0.controls)
summary(malic.control0.aov) # not sigificant between autoclaved and inoculated controls

<<<<<<< HEAD
=======

>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
# Week 2
wk2.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_2") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk2.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.control2.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk2.controls)
summary(malic.control2.aov) # not sigificant between autoclaved and inoculated controls

# Week 4
wk4.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_4") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk4.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.control4.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk4.controls)
summary(malic.control4.aov) # not sigificant between autoclaved and inoculated controls

# Week 6
wk6.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_6") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk6.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.control6.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk6.controls)
summary(malic.control6.aov) # not sigificant between autoclaved and inoculated controls

# Week 8
wk8.controls <- clusia.malic %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_8") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk8.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.control8.aov <- aov(MalicAverage ~ Condition * Treatment, data = wk8.controls)
summary(malic.control8.aov) # not sigificant between autoclaved and inoculated controls

# removing Control Mock & fixing 'Null isolates'
clusia.malic <- clusia.malic %>% 
  filter(Treatment != "Control Mock")
<<<<<<< HEAD
=======
View(clusia.malic)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

clusia.malic$Treatment[clusia.malic$Treatment == "Null Isolates"] <- "Nonfunctional Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "Null_Isolates"] <- "Nonfunctional Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "All_Isolates"] <- "All Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "Drought_Isolates"] <- "Drought Isolates"
clusia.malic$Treatment[clusia.malic$Treatment == "Phosphorus_Isolates"] <- "Phosphorus Isolates"

<<<<<<< HEAD
=======
View(clusia.malic)

>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
# arranging by Week, Water, and Treatment
clusia.malic <- clusia.malic %>% 
  arrange(Week, Condition, Treatment)
```

<<<<<<< HEAD
### Malic Acid Summary Stats
=======
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
```{r Summary Statistics - Malic Acid}
malic.sum <- clusia.malic %>% 
  group_by(Week, Condition, Treatment) %>% 
  summarise(n = n(),
            mean_malic = mean(MalicAverage, na.rm = TRUE),
            sd_malic = sd(MalicAverage, na.rm = TRUE),
            se = sd(MalicAverage, na.rm = TRUE)/sqrt(n()))
View(malic.sum)
```

<<<<<<< HEAD
### Malic Acid ANOVAs
=======
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
```{r Malic Acid ANOVAs}
# Week 0
malic.wk0 <- clusia.malic %>% 
  filter(Week == "Wk_0")
<<<<<<< HEAD
=======
View(malic.wk0)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.wk0.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk0)
summary(malic.wk0.aov) # not sigificant between treatment

# Week 2
malic.wk2 <- clusia.malic %>% 
  filter(Week == "Wk_2")
<<<<<<< HEAD
=======
View(malic.wk2)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.wk2.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk2)
summary(malic.wk2.aov) # significant drought effect

# Week 4
malic.wk4 <- clusia.malic %>% 
  filter(Week == "Wk_4")
<<<<<<< HEAD
=======
View(malic.wk4)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.wk4.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk4)
summary(malic.wk4.aov) # sigificant drought effect

# Week 6
malic.wk6 <- clusia.malic %>% 
  filter(Week == "Wk_6")
<<<<<<< HEAD
=======
View(malic.wk6)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

malic.wk6.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk6)
summary(malic.wk6.aov) # sigificant drought effect

# Week 8
malic.wk8 <- clusia.malic %>% 
  filter(Week == "Wk_8")
<<<<<<< HEAD

malic.wk8.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk8)
summary(malic.wk8.aov) # significant drought effect and microbial effect

TukeyHSD(malic.wk8.aov)
```


```{r Malic Acid Boxplot}
clusia.boxplot <- ggplot(data = clusia.malic, aes(x = Treatment, y = MalicAverage, fill = Condition)) + geom_boxplot() + geom_point(aes(fill = Condition), size = 2, shape = 21, position = position_jitterdodge()) + facet_grid(. ~ Week) 

clusia.boxplot <- clusia.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.095, 0.9))

clusia.boxplot <- clusia.boxplot + ylab(expression(Malic~Acid~Concentration~(mu~mol~H~g^{-1})))
=======
View(malic.wk8)

malic.wk8.aov <- aov(MalicAverage ~ Condition * Treatment, data = malic.wk8)
summary(malic.wk8.aov) # significant drought effect and microbial effect
```

```{r Malic Acid Boxplot}
clusia.boxplot <- ggplot(data = clusia.malic, aes(x = Treatment, y = MalicAverage, fill = Condition)) + geom_boxplot() + geom_point(aes(fill = Condition), size = 2, shape = 21, position = position_jitterdodge()) + facet_grid(. ~ Week) 

clusia.boxplot <- clusia.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.06, 0.9))
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

pdf("MalicAcid_Boxplot.pdf")
plot(clusia.boxplot)
dev.off()
```

<<<<<<< HEAD
At Week 0, both well-watered and drought plants show no difference in malic acid concentrations as expected. However, as the drought trial progresses, well-watered plants and drought plants begin to diverge significantly at Week 2 (p-value < 0.001). Higher amounts of malic acid in well-watered plants indicate higher CAM activity, which is in contrast with hypotheses that CAM activity would be highest in drought plants due to experiencing drought stress. Furthermore, there was no significant effect of microbial community until the last week (p- value < 0.05) with no interaction term, suggesting that availability of water is still the dominant driver of malic acid concentration. Tukeys HSD results indicate that although the differences in microbial communities are different, that these differences are occuring between well-watered microbial communities versus droughted microbial communities, verifying that the water availability is driving differences between plants and not the composition of the the microbial communities themselves. 

## Lipid Peroxidation Assay
```{r Importing Lipid Peroxidation Data}
clusia.lipid <- read.csv("~/Documents/Git/clusia_droughtexperiment/LipidPeroxidation.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
```
### Lipid Peroxidation Controls
=======
# Lipid Peroxidation Assay
```{r Importing Lipid Peroxidation Data}
clusia.lipid <- read.csv("~/Documents/Git/clusia_droughtexperiment/LipidPeroxidation.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
View(clusia.lipid)
str(clusia.lipid)
```

>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
```{r Lipid Peroxidation Controls}
# Week 0
wk0.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_0") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk0.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

lipid.control0.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk0.controls)
summary(lipid.control0.aov) # not sigificant between autoclaved and inoculated controls

<<<<<<< HEAD

=======
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
# Week 2
wk2.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_2") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk2.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

lipid.control2.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk2.controls)
summary(lipid.control2.aov) # not sigificant between autoclaved and inoculated controls

# Week 4
wk4.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_4") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk4.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

lipid.control4.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk4.controls)
summary(lipid.control4.aov) # not sigificant between autoclaved and inoculated controls

# Week 6
wk6.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_6") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk6.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

lipid.control6.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk6.controls)
summary(lipid.control6.aov) # not sigificant between autoclaved and inoculated controls

# Week 8
wk8.controls <- clusia.lipid %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_8") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk8.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

lipid.control8.aov <- aov(LipidPerox ~ Condition * Treatment, data = wk8.controls)
summary(lipid.control8.aov) # not sigificant between autoclaved and inoculated controls

# removing Control Mock
clusia.lipid <- clusia.lipid %>% 
  filter(Treatment != "Control Mock")
View(clusia.lipid)

# arranging by Week, Water, and Treatment
clusia.lipid <- clusia.lipid %>% 
  arrange(Week, Condition, Treatment)
```

<<<<<<< HEAD
### Lipid Peroxidation Summary Stats
```{r Lipid Summary}
=======
```{r Summary Statistics - LipidPerox}
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
lipid.sum <- clusia.lipid %>% 
  group_by(Week, Condition, Treatment) %>% 
  summarise(n = n(),
            mean_lipid = mean(LipidPerox, na.rm = TRUE),
            sd_lipid = sd(LipidPerox, na.rm = TRUE),
            se = sd(LipidPerox, na.rm = TRUE)/sqrt(n()))
View(lipid.sum)

lipid.errobars <- ggplot(data = lipid.sum, aes(x = Treatment, y = mean_lipid, fill = Condition)) + geom_bar(stat = "identity", color = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = mean_lipid-sd_lipid, ymax = mean_lipid+sd_lipid), width = 0.2, position = position_dodge(0.9)) + facet_grid(. ~ Week)

<<<<<<< HEAD
lipid.errobars <- lipid.errobars + theme_bw() + scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.1, 0.8)) + ylab(expression(Mean~Lipid~Peroxidation~(nmol~MDA~g^{-1})))

lipid.errobars
```

### Lipid Peroxidation ANOVAs
```{r Weekly Lipid ANOVAs}
# Week 0
lipid.wk0 <- clusia.lipid %>% 
  filter(Week == "Wk_0")
=======
lipid.errobars <- lipid.errobars + theme_bw() + scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.1, 0.8))
```

```{r ANOVAs - LipidPerox}
# Week 0
lipid.wk0 <- clusia.lipid %>% 
  filter(Week == "Wk_0")
View(lipid.wk0)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

lipid.wk0.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk0)
summary(lipid.wk0.aov) 

# Week 2
lipid.wk2 <- clusia.lipid %>% 
  filter(Week == "Wk_2")
<<<<<<< HEAD
=======
View(lipid.wk2)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

lipid.wk2.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk2)
summary(lipid.wk2.aov)

# Week 4
lipid.wk4 <- clusia.lipid %>% 
  filter(Week == "Wk_4")
<<<<<<< HEAD
=======
View(lipid.wk4)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

lipid.wk4.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk4)
summary(lipid.wk4.aov) 

# Week 6
lipid.wk6 <- clusia.lipid %>% 
  filter(Week == "Wk_6")
<<<<<<< HEAD

lipid.wk6.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk6)
summary(lipid.wk6.aov)
=======
View(lipid.wk6)

lipid.wk6.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk6)
summary(lipid.wk6.aov) # significant <0.1 microbial effect
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

# Week 8
lipid.wk8 <- clusia.lipid %>% 
  filter(Week == "Wk_8")
<<<<<<< HEAD

lipid.wk8.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk8)
summary(lipid.wk8.aov) # significant drought effect, significant microbial effect

TukeyHSD(lipid.wk8.aov)
=======
View(lipid.wk8)

lipid.wk8.aov <- aov(LipidPerox ~ Condition * Treatment, data = lipid.wk8)
summary(lipid.wk8.aov) # significant drought effect, significant microbial effect
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
```

```{r Lipid Peroxidation Boxplot}
lipid.boxplot <- ggplot(data = clusia.lipid, aes(x = Treatment, y = LipidPerox, fill = Condition)) + geom_boxplot() + geom_point(aes(fill = Condition), size = 2, shape = 21, position = position_jitterdodge()) + facet_grid(. ~ Week) 

<<<<<<< HEAD
lipid.boxplot <- lipid.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.1, 0.8)) + ylab(expression(Lipid~Peroxidation~(nmol~MDA~g^{-1})))
=======
lipid.boxplot <- lipid.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.1, 0.8))
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

pdf("LipidPerox_Boxplot.pdf")
plot(lipid.boxplot)
dev.off()
```

<<<<<<< HEAD
Lipd peroxidation did not differ signifcantly between well-watered plants and drought plants until the final week of the experiment. Overall, plants inoculated with all beneficial isolates (All Isolates) differed from control plants (Control), plants that received autoclaved bacteria (Control Mock), and plants that received isolates with no measured function (Nonfunctional) (p-value < 0.05). The greatest differences in lipid peroxidation occured between well-watered plants and drought plants, indepent of microbial community. Although there is a significant microbial effect (p-value < 0.01), there is no interaction term suggesting that lipid peroxidation in drought conditions is not tied to microbial community composition despite the general differences between plants incolated with beneficial isolates and those of the control.  





## Proline Assay
```{r Importing Proline Data}
clusia.proline <- read.csv("~/Documents/Git/clusia_droughtexperiment/Proline.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
```

### Proline Controls
```{r Proline Controls}
=======
# Proline Assay
```{r Importing Proline Data}
clusia.proline <- read.csv("~/Documents/Git/clusia_droughtexperiment/Proline.csv", header = TRUE , sep = ",", stringsAsFactors = TRUE, na.strings = "na")
View(clusia.proline)
str(clusia.proline)
```

```{r Checking Controls - Proline}
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
# Week 0
wk0.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_0") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk0.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

proline.control0.aov <- aov(Proline ~ Condition * Treatment, data = wk0.controls)
summary(proline.control0.aov) # not sigificant between autoclaved and inoculated controls

# Week 2
wk2.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_2") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk2.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

proline.control2.aov <- aov(Proline ~ Condition * Treatment, data = wk2.controls)
summary(proline.control2.aov) # not sigificant between autoclaved and inoculated controls

# Week 4
wk4.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_4") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk4.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

proline.control4.aov <- aov(Proline ~ Condition * Treatment, data = wk4.controls)
summary(proline.control4.aov) # significant interaction term + significant at < 0.1 for drought and microbial effect

# Week 6
wk6.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_6") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk6.controls)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

proline.control6.aov <- aov(Proline ~ Condition * Treatment, data = wk6.controls)
summary(proline.control6.aov) # significant drought effect

# Week 8
wk8.controls <- clusia.proline %>% 
  filter(Treatment == "Control" | Treatment == "Control Mock") %>% 
  filter(Week == "Wk_8") %>% 
  arrange(Condition, Treatment)
<<<<<<< HEAD
=======
View(wk8.controls)

>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
proline.control8.aov <- aov(Proline ~ Condition * Treatment, data = wk8.controls)
summary(proline.control8.aov) # significant drought effect

# removing Control Mock & fixing 'Null isolates'
clusia.lipid <- clusia.lipid %>% 
  filter(Treatment != "Control Mock")
<<<<<<< HEAD
=======
View(clusia.lipid)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

# arranging by Week, Water, and Treatment
clusia.lipid <- clusia.lipid %>% 
  arrange(Week, Condition, Treatment)
```
<<<<<<< HEAD
### Proline Summary Stats
=======

>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
```{r Summary Statistics - Proline}
proline.sum <- clusia.proline %>% 
  group_by(Week, Condition, Treatment) %>% 
  summarise(n = n(),
            mean_proline = mean(Proline, na.rm = TRUE),
            sd_proline = sd(Proline, na.rm = TRUE),
            se = sd(Proline, na.rm = TRUE)/sqrt(n()))
View(proline.sum)

proline.errobars <- ggplot(data = proline.sum, aes(x = Treatment, y = mean_proline, fill = Condition)) + geom_bar(stat = "identity", color = "black", position = position_dodge(0.9)) + geom_errorbar(aes(ymin = mean_proline-sd_proline, ymax = mean_proline+sd_proline), width = 0.2, position = position_dodge(0.9)) + facet_grid(. ~ Week)

<<<<<<< HEAD
proline.errobars <- proline.errobars + theme_bw() + scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.09, 0.85)) + ylab(expression(Mean~Proline~Concentration(mu~moles~g^{-1})))

proline.errobars
```

### Proline ANOVAs
=======
proline.errobars <- proline.errobars + theme_bw() + scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.09, 0.85))
```

>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
```{r ANOVAs - Proline}
# Week 0
proline.wk0 <- clusia.proline %>% 
  filter(Week == "Wk_0")
<<<<<<< HEAD
=======
View(proline.wk0)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

proline.wk0.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk0)
summary(proline.wk0.aov) # no significance

# Week 2
proline.wk2 <- clusia.proline %>% 
  filter(Week == "Wk_2")
<<<<<<< HEAD
=======
View(proline.wk2)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

proline.wk2.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk2)
summary(proline.wk2.aov) # significant drought effect (<0.1) and interaction term (< 0.05)

# Week 4
proline.wk4 <- clusia.proline %>% 
  filter(Week == "Wk_4")
<<<<<<< HEAD
=======
View(proline.wk4)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

proline.wk4.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk4)
summary(proline.wk4.aov) # significant drought effect

# Week 6
proline.wk6 <- clusia.proline %>% 
  filter(Week == "Wk_6")
<<<<<<< HEAD

proline.wk6.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk6)
summary(proline.wk6.aov)  # significant drought effect (<0.001), microbial (<0.1), interaction (<0.1)
TukeyHSD(proline.wk6.aov)
=======
View(proline.wk6)

proline.wk6.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk6)
summary(proline.wk6.aov)  # significant drought effect (<0.001), microbial (<0.1), interaction (<0.1)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

# Week 8
proline.wk8 <- clusia.proline %>% 
  filter(Week == "Wk_8")
<<<<<<< HEAD
=======
View(proline.wk8)
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8

proline.wk8.aov <- aov(Proline ~ Condition * Treatment, data = proline.wk8)
summary(proline.wk8.aov) # significant drought effect (<0.001) and microbial effect (<0.1)
```

```{r Proline Boxplot}

proline.boxplot <- ggplot(data = clusia.proline, aes(x = Treatment, y = Proline, fill = Condition)) + geom_boxplot() + geom_point(aes(fill = Condition), size = 2, shape = 21, position = position_jitterdodge()) + facet_grid(. ~ Week) 

proline.boxplot <- proline.boxplot + theme_bw() +scale_fill_manual(values=c("indianred3", "cadetblue3"), breaks=c("Well-watered", "Drought"),labels=c("Well-watered", "Drought")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.title.x = element_blank()) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + theme(legend.position = c(0.09, 0.85))

pdf("Proline_Boxplot.pdf")
plot(proline.boxplot)
dev.off()

```
<<<<<<< HEAD

Water is predominantly the determinant of proline concentration, though not until Week 4. Unlike malic acid and lipid peroxidation, there is a slight influence of microbial community on proline in Week 6 and Week 8 (p-value < 0.1), though Tukeys HSD shows that these differences are the result of differences between well-watered communities and droughted communities. Therefore, the significant interaction term is not an indication that plants containing each constructed communities respond differently within the drought treatment. Well-watered plants have significantly lower amounts of proline than drought plants at Week 4 (p-value < 0.05), with the gap between the two widening over time. This is consistent with proline being a stress metabolite that increases in response to drought stress.
=======
>>>>>>> 02e0bce66b79471b865aaada76b52cb4560240f8
